HyperLogLog: Exponentially Bad in Adversarial Settings

### 2022-02-07 docs/HLL_exp_bad/main.tex
compressing table 4
better explanation of anomaly in S2 attack, Fig 3

Second, Figures~\ref{fig:graphS2},~\ref{fig:graphS4} show very close agreement between the predictions made by our analysis in Section~\ref{sec:nonempty} and our experimental results for the situation where the HLL sketch is initially non-empty. The only significant difference is in scenario S2, where there is a small increase in the cardinality estimate, around 1-2\% on average, as a result of the attack, whereas the theoretical analysis suggests there should be no increase. The reason for this is that the insertion of the initial random $2^{t-1} m\ln m$ items is not guaranteed to produce a situation in which every bucket contains a value $t$ or greater -- this condition holds only with high probability.

@@

\begin{table*}[tb!]
\begin{center}
\caption{Attack results for HLL in Redis, averaged over 50 iterations.}\label{table:tab3}
%\begin{tabular}{| m{11em} | m{4em} | m{4.2em} |}
\begin{tabular}{| c | r | r |}
    \hline
    \textbf{Scenario} &  \multicolumn{2}{c|}{S2} \\ \hline
    %\textbf{HLL initially empty?} & no & yes \\ \hline
    \textbf{Original Card. Est.} & 0 & 139,967 \\ \hline
     \textbf{$\epsilon$} &  0.5 & - \\ \hline
    \textbf{\# Items added} & 524,210 & 524,454\\ \hline
    \textbf{Final Card. Est.} & 13,185 & 139,967 \\ \hline
\end{tabular}
\end{center}
\end{table*}
%\todo[inline]{Results from Redis or GBQ if we get them.}

>>>>

Second, Figures~\ref{fig:graphS2},~\ref{fig:graphS4} show very close agreement between the predictions made by our analysis in Section~\ref{sec:nonempty} and our experimental results for the situation where the HLL sketch is initially non-empty. The only significant difference is in scenario S2, where there is a small increase in the cardinality estimate, around 1-2\% on average, as a result of the attack, whereas the theoretical analysis suggests there should be no increase. The reason for this is that the insertion of the initial random $2^{t-1} m\ln m$ items is not guaranteed to produce a situation in which every bucket contains a value $t$ or greater -- this condition holds only with high probability. The result is that some bucket contents are \emph{increased} to $t$ as a result of insertions during the course of the attack, leading to a slightly increased cardinality estimate.

@@

\begin{table*}[tb!]
\begin{center}
\caption{Attack results for HLL in Redis, scenario S2, averaged over 50 iterations.}\label{table:tab3}
%\begin{tabular}{| m{11em} | m{4em} | m{4.2em} |}
\begin{tabular}{| c | r | r |}
    \hline
    \textbf{Original Card. Est.} & 0 & 139,967 \\ \hline
     \textbf{$\epsilon$} &  0.5 & - \\ \hline
    \textbf{\# Items added} & 524,210 & 524,454\\ \hline
    \textbf{Final Card. Est.} & 13,185 & 139,967 \\ \hline
\end{tabular}
\end{center}
\end{table*}
%\todo[inline]{Results from Redis or GBQ if we get them.}
